---
title: "FARS-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FARS-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  comment = "#>"
)
library(TestPackage)
library(maps)
```
The `fars` package reads and maps Fatal Analysis Reporting System or short FARS data for various years. 

In the packages the data for the years 2013, 2014 and 2015 are included.

```{r}
list.files(system.file("extdata", package = "TestPackage"))
```

## Package Functions

This pacakge provides various functions to work with the data files.

1. `make_filename`
This function returns file name and path to the data files:

```{r}
yr <- 2015
make_filename(yr)
```

2. `fars_read_years`
This is just a helping function and should not be used on its own.

3. `fars_summarize_years`
This function summarizes accidents data of a given year by month. 

```{r}
yr <- 2015
fars_summarize_years(yr)
```

4. `fars_map_state`
This function generates a map plot showing accident locations by the given year and state number.

```{r}
state_num <- 49 # Utah
yr <- 2014
fars_map_state(state_num, yr)
```
